Multiplex stream graphs

### 2019-04-18 tex/main.tex
Update main.tex

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{xcolor}

@@

    We define a multiplex stream graph as a tuple $M = (T_M, V_M, W_M, E_M, T, V, {\cal L})$, such that $T_M \subseteq T$, $V_M \subseteq V \times {\cal L}$, $W_M \subseteq T_M\times V_M$ and $E_M\subseteq T_M \times V_M \otimes V_M$.
    $T$ and $V$ are, respectively, a time interval and a set of nodes, just like in stream graphs.
    We then define {\em layers}; a multiplex stream graph can have an arbitrary number $d$ of aspects, and we define ${\cal L}$, as $\{L_i\}_{i=0}^{d}$ the set of layers, such that there is one layer for each $i=0..d$.
    Notice that just like in multiplex networks, nodes in time ({\em i.e.}, elements of $W_M$) can be present in an arbitrary number of layers.

    \tiph{Je ne suis pas sûre que l'on aie besoin de $V_M$, en fait; toute l'info de présence des n\oe{}uds dans les couches peut être contenue dans $W_M$ ?}
    \pimprenelle{Je ne sais pas, ça dépend de si on considère qu'un n\oe{}ud qui n'apparait à aucun temps t dans une couche existe dans cette couche ou pas : on pourrait avoir un n\oe{}ud qui apparait dans $V_M$ et pas dans $W_M$ même si c'est tordu ... et puis à ce moment là même dans un stream graph classique $S=(T,V,W,E)$, est-ce qu'on pourrait pas se dire que de la même façon que V n'est pas "utile" en terme d'informations supplémentaires ?}
    \pimprenelle{Je ne vois pas bien ce que représente la variable $T_M$ par rapport à la variable $T$ ? est-ce que les layers elle-mêmes seraient dépendantes du temps ? 
    Proposition : $T_M$ is a set of $T_i \subseteq T$.}

	\pimprenelle{Il y a une subtilité sur les layers : an aspect $(i)$ is a set $L_i$ of  elementary layers $\alpha^{i}_1,\dots,\alpha^{i}_n$
    		 a layer $\alpha$ is an combination of elementary layer of each aspect : $\alpha \in L_1\times\dots\times L_d$
   	}

    From this definition, let us define common streams of interest.
    For any layer $i \in {\cal L}$, the {\em intra-layer} stream graph $S^{(i)}$ is the stream such that ...

	\pimprenelle{Suggestion :}
	For any layer $\alpha \in L_1 \times \dots \times L_d$, the {\em intra-layer} stream graph $S^{\alpha}$ is the stream $S^{\alpha}=(T,V^{\alpha},W^{\alpha},E^{\alpha})$ such that for all $t$ in T :
	\begin{itemize}
		\item $V^{\alpha}$ is the set of nodes $(u,\alpha) \in V_M$
		\item $W^{\alpha}$ is the set of $(t,u,\alpha)$ included in $W_M$. 
		\item $E^{\alpha}$ is the set of links $(t,(u,\alpha),(v,\alpha))$ included in $E_M$.		
	\end{itemize}

	\pimprenelle{fin}

    For any two layers $i,j\in {\cal L}$, the {\em inter-layer} stream graph $S^{(i,j)}$ ...
	\pimprenelle{Suggestion}
	For any two layers $\alpha, \beta \in L_1\times \dots\times L_d$, the {\em inter-layer} stream graph is the stream $S^{\alpha,\beta} = (T, V^{(\alpha,\beta)},W^{(\alpha,\beta)},E^{(\alpha,\beta)})$ such that :
	\begin{itemize}
		\item $V^{(\alpha,\beta)} = \{(u,\gamma) | u \in V, \gamma \in \{\alpha,\beta\} \} \cap V_M$
		\item $W^{(\alpha,\beta)}= \{(t,u,\gamma) | u \in V, \gamma \in \{\alpha,\beta\} \} \cap W_M$
		\item $E^{(\alpha,\beta)} = \{(t,(u,\alpha),(v,\beta) | u,v \in V\} \cap E_M $
	\end{itemize}
	\pimprenelle{fin}
    Notice that for any layer $i$, $S^{(i)}$ is equivalent to $S^{(i,j)}$.
    \pimprenelle{du coup je ne comprends pas...}

    The {\em coupling} ...

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{xcolor}
\usepackage{amsthm}

\newtheorem{thm}{Theorem}
\newtheorem{prop}{Propery}

\theoremstyle{definition}
\newtheorem{defn}{Definition}

\theoremstyle{remark}
\newtheorem{rmq}{Remark}

@@

	\pimprenelle{Multilayer stream graphs serait peut etre plus général ?}

    We define a multiplex stream graph as a tuple $M = (T,T_M,V,W_M,E_M,{\cal L})$, such that $T$ and $V$ are, respectively, a time interval and a set of nodes, just like in stream graphs. 
    As in multilayer graphs, ${\cal L}$ is a set of $d$ {\em aspects}; ${\cal L} = \{L_i\}_{i=1}^d$, and an element $\alpha_i$ of $L_i$ is named {\em elementary layer}. An element of $L=L_1\times \dots \times L_d$ is named {\em layer}. From those elements, $V_M$ is defined as follows : $V_M = \{ (u,\alpha), u\in V, \alpha \in L\}$ .

	$T_M$ is a set of intervals of $T$ so for that each layer $\alpha$, $T_{\alpha}$ is the interval at which the layer exists.

	$W_M \subseteq T\times V \times (L_1 \times \dots \times L_d)$ represents the existing points on layers with respect to the time.

   $E_M \subseteq T\times V_M \otimes V_M$ are the links appearing with respect to time.

    Notice that just like in multiplex networks, nodes in time ({\em i.e.}, elements of $W_M$) can be present in an arbitrary number of layers.

    From this definition, let us define common streams of interest.

	For any layer $\alpha \in L_1 \times \dots \times L_d$, the {\em intra-layer} stream graph $S^{\alpha}$ is the stream $S^{\alpha}=(T^{\alpha},V^{\alpha},W^{\alpha},E^{\alpha})$ such that for all $t$ in T :
	\begin{itemize}
		\item $T^{\alpha} \in T_M$
		\item $V^{\alpha} =\{(u,\alpha),u\in V\} \cap V_M$
		\item $W^{\alpha} =\{(t,u,\alpha),|u\in V, t \in T \} \cap W_M$ 
		\item $E^{\alpha} = \{(t,(u,\alpha),(v,\alpha))| t \in T,(u,v)\in V^2 \} \cap E_M$.		
	\end{itemize}

	For any two layers $\alpha, \beta \in L_1\times \dots\times L_d$, the {\em inter-layer} stream graph is the stream $S^{(\alpha,\beta)} = (T, V^{\alpha,\beta},W^{\alpha,\beta},E^{\alpha,\beta})$ such that :
	\begin{itemize}
		\item $T^{\alpha,\beta}=T^{\alpha}\cap T^{\beta}$
		\item $V^{\alpha,\beta} = \{u,\gamma | u \in V, \gamma \in \{\alpha,\beta\} \} \cap V_M$
		\item $W^{\alpha,\beta}= \{(t,u,\gamma) | u \in V, \gamma \in \{\alpha,\beta\} \} \cap W_M$
	    \item $E^{\alpha,\beta} = \{(t,(u,\alpha),(v,\beta) | u,v \in V\} \cap E_M $
	\end{itemize}

	    Notice that for any layer $\alpha$, $S^{(\alpha)}$ is equivalent to $S^{(\alpha,\alpha)}$.

	The {\em intersection} of two substreams $S_1$ and $S_2$ is defined as follows :
	\[
		S' = S_1 \cap S_2 = (T_1\cap T_2, V_1 \cap V_2, W_1 \cap W_2, E_1\cap E_2) 
	\]

	Notice that this intersection is a stream graph too.

	The {\em union} of two substreams $S_1$ and $S_2$ is defined as follows :
	\begin{align*}
		S' = S_1 \cup S_2 = (T', V_1 \cup V_2, W_1 \cup W_2, E' \})\\
		T' = [\min(T_1,T_2),\max(T_1,T_2)]\\
		E' = E_1 \cup E_2 \cup (T'\times V_1 \times V_2 \cap E )
	\end{align*}

	Notice that the union of two sub stream graphs gives a stream graph.

	\begin{prop}
		\[
			\bigcup_{(\alpha,\beta) \in L^2} S^{(\alpha,\beta)} = S
		\]
	\end{prop}

    The {\em coupling edges} are $E_C=\{(t,u,\alpha,v,\beta)\in E_M | u=v\}$.

    The {\em intra-layer edges} are $E_I = \{(t,u,\alpha,v,\beta) \in E_M | \alpha = \beta \}$

    The {\em inter-layer edges} are $\bar{E_I} = E_M\backslash E_I$.

   	The {\em multilayer graph at time t} $M_t$ is $M_t = (V_{M,t}, E_{M,t},V_t,{\cal L}_t)$ with : 
    \begin{itemize}
		\item $V_{M,t} = \{(u,\alpha)| (t,u,\alpha)\in W_M\}$
		\item $E_{M,t} = \{(u,\alpha,v,\beta) | (t,u,\alpha,v,\beta) \in E_M\}$
		\item $V_t = {u | (t,u) \in V}$
		\item ${\cal L}_t = {L_i,t}_{i=1}^d, L_{i,t}=(\alpha)_i, t\in T_\alpha$
    \end{itemize}

    \begin{rmq}
    	We assume that $\forall (i,t), \; L_{(i,t)} \neq \emptyset$.
    \end{rmq}

@@

    \section{Intrications (Etranglement)}
